Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-24 cordillera-cycle.tex
Rev. Stumpf: update to a larger location map.

\begin{figure}%
\includegraphics{locmap}
\caption{%
      Relief map of northern North America showing a~reconstruction of the
      areas once covered by the Cordilleran (CIS), Laurentide (LIS),
      Innuitian (IIS), and Greenland (GIS) ice sheets during the last
      18\,\unit{\chem{^{14}C}\,ka} \citep[21.4\,cal\,ka,][]{Dyke.2004}. The
      rectangular box denotes the location of the modelling domain used in
      this study. Major mountain ranges covered by the ice sheet include the
      Alaska Range (AR), the Wrangell and Saint Elias mountains (WSEM), the
      Selwyn and Mackenzie mountains (SMKM), the Skeena Mountains (SM), the
      Coast Mountains (CM), the Columbia and Rocky Mountains (CRM), and the
      North Cascades (NC). Major depressions include the Liard Lowland (LL),
      the Interior Plateau of British Columbia (IP), and the Puget Lowland
      (PL). The background map consists of ETOPO1 \citep{Amante.Eakins.2009}
      and Natural Earth Data \citep{Patterson.Kelso.2015}.}
\label{fig:locmap}%
\end{figure}%

>>>>

\begin{figure*}%
\includegraphics{locmap}
\caption{%
      Relief map of the northern American Cordillera showing cumulative last
      glacial maximum ice cover between 21.4 and
      16.8\,\unit{\chem{^{14}C}\,cal\,ka} \citep[red line]{Dyke.2004}, and
      the modelling domain used in this study (black rectangle). The
      background map consists of ETOPO1 \citep{Amante.Eakins.2009} and
      Natural Earth Data \citep{Patterson.Kelso.2015}.}
\label{fig:locmap}%
\end{figure*}%
